### 2022-12-01 ms.rmd
Adding trait random effect. I suspect it will explain a lot of variation.

##################################################
# Model 1.1: Intercept only model. 
##################################################
rerun = TRUE
if(rerun){
  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data) 
  # Save model1.1
  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
} else{ model1.1 <- readRDS("./output/models/lnRRQ10_1.1")}

@@

if(rerun){
  # More realistic model with 
  model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)

@@

# R2
fix <- var(predict(model1.2_bayes)[,"Estimate"])
r2_ml(model1.2)

# Orchard plot
results1.2 <- mod_results(model1.2, mod = "habitat", group  = "record_num", at = list(type = c("acute", "acclim")), by = "type", weights = "prop", data = lnRRQ10_data)

####################################################
# Model 1.3's: Trait type varied by acclimation type
# but data is seperated by habitat to simplify
####################################################
 if(rerun){
  # Filter to different habitats
   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m")
   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f")
   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t")

@@

   # More realistic model with traits in marine species
  model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = m_phylo), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_m)

   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) + (1|obs), data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_m)

    # More realistic model with traits in freshwater species
  model1.3_f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full =f_phylo), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_f)

   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|obs), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_f)

    # More realistic model with traits in terrestrial species
  model1.3_t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full =t_phylo), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_t)

   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1|obs), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)

@@

###################################################
# Model 2.1: Intercept only model.
# Used for heterogeneity analysis
###################################################
rerun = TRUE
if(rerun){
  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data)

  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)

@@

if(rerun){
  # More realistic model 
  model2.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data)

   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)

>>>>

##################################################
# Model 1.1: Intercept only model. 
##################################################
rerun = TRUE
if(rerun){
  model1.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

  model1.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)

  # Save model1.1
  saveRDS(model1.1, file = "./output/models/lnRRQ10_1.1")
  saveRDS(model1.1_bayes, file = "./output/models/lnRRQ10_1.1_bayes")
} else{ 
  model1.1 <- readRDS("./output/models/lnRRQ10_1.1")
model1.1_bayes <- readRDS("./output/models/lnRRQ10_1.1_bayes")}

@@

if(rerun){
  # More realistic model with 
  model1.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor), dfs = "contain", 
                              test = "t", data = lnRRQ10_data)

   model1.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data)

@@

####################################################
# Model 1.3's: Trait type varied by acclimation type
# but data is separated by habitat to simplify
####################################################
 if(rerun){
  # Filter to different habitats
   lnRRQ10_data_m <- lnRRQ10_data %>% filter(habitat == "m")
   lnRRQ10_data_f <- lnRRQ10_data %>% filter(habitat == "f")
   lnRRQ10_data_t <- lnRRQ10_data %>% filter(habitat == "t")

@@

   # More realistic model with traits in marine species
  model1.3_m <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full = m_phylo), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_m)

   model1.3_m_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_m)) + (1 | spp) +(1|trait) + (1|obs), data2 = list(A_m=A_m), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_m)

    # More realistic model with traits in freshwater species
  model1.3_f <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full =f_phylo), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_f)

   model1.3_f_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_f)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_f=A_f), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_f)

    # More realistic model with traits in terrestrial species
  model1.3_t <- metafor::rma.mv(effect_size ~  c_accl_time + type + trait_category + type:trait_category, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full =t_phylo), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_t)

   model1.3_t_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + trait_category + type:trait_category + (~1 | record_num) + (1 | gr(species_full, cov = A_t)) + (1 | spp) + (1 | trait) + (1|obs), data2 = list(A_t=A_t), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnRRQ10_data_t)

@@

###################################################
# Model 2.1: Intercept only model.
# Used for heterogeneity analysis
###################################################
rerun = TRUE
if(rerun){
  model2.1 <- metafor::rma.mv(effect_size ~ 1, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data)

  model2.1_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  1 + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A_CVR=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)

@@

if(rerun){
  # More realistic model 
  model2.2 <- metafor::rma.mv(effect_size ~  c_accl_time + type + habitat + type:habitat, V = V, 
                              random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | spp,
                                            ~1 | trait,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_CVR), dfs = "contain", 
                              test = "t", data = lnCVRQ10_data)

   model2.2_bayes <- brms::brm(effect_size | se(sqrt(V)) ~  c_accl_time + type + habitat + type:habitat + (~1 | record_num) + (1 | gr(species_full, cov = A_CVR)) + (1 | spp) + (1|trait) + (1|obs), data2 = list(A=A_CVR), family = gaussian(), prior = c(prior(normal(0, 10), "Intercept"), prior(student_t(3, 0, 10), "sd")), control = list(adapt_delta = 0.98, max_treedepth = 12), chains = 4, thin = 5, iter = 5000, warmup = 1000, cores = 4, data = lnCVRQ10_data)
